Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2021-12-11 jas_response.tex
Update response

Dumbell is a decent approximation for a rigid spacecraft.
Can easily extend from a dumbell, 2 masses to arbitary number of masses to handle more general spacecraft. 
In the limit an arbitrary number of masses can then approximate a general rigid body.

@@

Inertial positions not required.

Add relative equations of motions

The formulation presented assumes that the inertial orentation of the asteroid is available.

@@

@@

@@

@@

@@

Add additional detail on limitations. 
Ground based sensors are also limited in number, in disrepair and over taxed (cite a reference on the DSN/Arecibo collapsing)

\comment{
Page 4 line 7, "onboard" as opposed to "onborad".
}

\comment{
Page 4, line 37, "During this simulation, this update shape model is then used in a nonlinear controller...". The second "this" should not have a capital "T", and should be "used in" as opposed to "used to in" .
}

\comment{
Page 8, line 1-2, the authors should augment the statement made citing reference 7 with one or two sentences for the unfamiliar reader.  
}

@@

Good catch. 
Don't actually simulate time of flight of a sensor. 
instead utilizing ray intersection algorithms to determine distance. 
This equation used to relate distance in simulation to a time of flight as would be measured in reality.

>>>>

The use of the dumbbell approximation allows use to avoid having to evaluate the integral over the extended body in the equations of motion.
The dumbbell model allows us to approximate an extended body with a miminimum of additional complexity.
Additional comments have been added to the manuscript explaining this decision and copied here.

The dumbbell is in some sense the simplest approximation of an extended rigid body.
It allows for simple analytical solution for the moment of inertia and greatly simplifies the equations of motion.
Dumbell is an approximation for a rigid spacecraft and is used widely 
Can easily extend from a dumbell, 2 masses to arbitary number of masses to handle more general spacecraft. 
In the limit an arbitrary number of masses can then approximate a general rigid body.

@@

In our analyis, we have assumed that the inertial position of both the asteroid and vehicle are available.
For both bodies we assume that ground based tracking/orbit determination is available prior to arrival.
This provides the inertial state of both bodies and is a requirement for the orbital rendezvous prior to any surface mapping operation.
Additional comments have been added to the manuscript and are repeated here.

@@

Thank you for the comments aimed at improving the quality of the manuscript. 
Additional references and discussion related to more recent missions have been included.

In addition, additional detail concerning spacecraft/state uncertainties and perturbing forces has been added to the manuscript.
The discussion discusses the current limitations of the presented approach and discuses this as an area of future work.
The additional discussion is presented here.

@@

Thank you for this comment. 
We have replaced ''dynamic`` with ''dynamical`` in several locations throughout the manuscript.
We do not repeat the corrections here for simplicity.

@@

Depending on the specific mission objectives the preliminary mapping phase may serve multiple purposes. 
In this week, we seek to utilize the mapping phase to create a polyhedron potential model and select an appropriate landing site. 
We added additional discussion related to more recent missions and copied below.

@@

The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REX mission has been incorporated.
The additional discussion has been copied below.

@@

This sentence has been removed and replaced with the following:

Onboard shape reconstruction techniques enable autonomous operations which allow for a greater range of spacecraft operations.

\comment{
Page 4 line 7, "onboard" as opposed to "onborad".
}
This typo has been corrected and is copied below.

\comment{
Page 4, line 37, "During this simulation, this update shape model is then used in a nonlinear controller...". The second "this" should not have a capital "T", and should be "used in" as opposed to "used to in" .
}
This typo has been corrected and is copied below.

\comment{
Page 8, line 1-2, the authors should augment the statement made citing reference 7 with one or two sentences for the unfamiliar reader.  
}
Additional detail describing the polyhedron potential model is added and copied below.

The polyhedron potential model is based on a triangular faceted shape model of an asteroid.
In this approach, the shape of the asteroid is used to directly compute the exterior potential.

@@

The equation has been corrected and is copied below.
